% Preamble
% ---
\documentclass[9pt,oneside]{memoir}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage[T1]{fontenc}
\usepackage{scrextend}
\usepackage{calc}
\usepackage{tabularx}

\pagestyle{empty}
\geometry{letterpaper,tmargin=.5in,bmargin=.5in,lmargin=.5in,rmargin=.5in,headheight=0in,headsep=0in,footskip=.3in}

\setlength{\parindent}{0in}
\setlength{\parskip}{0in}
\setlength{\itemsep}{0in}
\setlength{\topsep}{0in}
\setlength{\tabcolsep}{0in}

\newcommand{\name}{Clay McGinnis}
\newcommand{\email}{mcginnis@clay.sh}
\newcommand{\github}{https://github.com/ClayMav}
\newcommand{\website}{https://clay.sh}

\newcommand{\cgpa}{3.5}


\begin{document}
\fontfamily{ppl} \selectfont

\begin{center}
      \textbf{\HUGE{\name}}\\
      \vspace{2px}
      \email\hspace*{10px}::\hspace*{10px}\url{\website}\hspace*{10px}::\hspace*{10px}\url{\github}\\
\end{center}

\vspace{3pt} \rule{\textwidth}{1pt}\vspace{6pt}

\textbf{Objective:} To obtain a full time Software Engineering job in
the Early Spring of 2020.

\vspace*{-8px}
\subsection*{Education:}

\begin{itemize}
      \item[] Missouri University of Science and Technology (Missouri S\&T)
            \hfill \textbf{December 2020}\\
            \textbf{B.S. Computer Science}
            \hfill \cgpa{} Cumulative GPA
      \item[] \textbf{Relevant Courses:} Software Engineering, Operating Systems,
            Algorithms, Data Structures, Databases, Data Mining, Artificial Intelligence
\end{itemize}

\vspace*{-11px}
\subsection*{Experience:}

\begin{itemize}
      \item[] \textbf{Amazon.com}
            \hfill Seattle, WA\\
            \textit{\textbf{Software Development Engineer Intern}}
            \hfill May. 2020 --- Aug. 2020
            \begin{itemize}
                  \item[\textbullet] Modernized metrics publishing to be more granular resulting
                        in diagnostics for hundreds of thousands of service calls
                  \item[\textbullet] Created dashboard for diagnosing slowdowns and errors utilizing
                        newly acquired data
            \end{itemize}

      \item[] \textbf{CEADS-LIN:\@ Cybersecurity and Evolutionary Computing Research}
            \hfill Rolla, MO\\
            \textit{\textbf{Research Assistant} with Dr. Daniel Tauritz}
            \hfill Feb. 2018 --- Aug. 2019
            \begin{itemize}
                  \item[\textbullet] Built visualization tools in React.js to
                        monitor containerized network traffic and analyze evolutionary experiments
                        in real time
                  \item[\textbullet] Contributed to academic papers describing how our
                        platform detects network defense strategies
            \end{itemize}

      \item[] \textbf{Multirotor Robot Design Team}
            \hfill Rolla, MO\\
            \textit{\textbf{Chief Software Engineer}}
            \hfill Feb. 2019 --- May 2020
            \begin{itemize}
                  \item[\textbullet] Managed a team of 30+ software developers in
                        creating real-time autonomous software for an octo-copter resulting in
                        acceptance to the International Aerial Robotics Competition
                  \item[\textbullet] Coordinated real-time, high speed artificial intelligence for an
                        octo-copter flying at 70 mph using a state-machine and multithreading
            \end{itemize}

      \item[] \textbf{Edward Jones Investments}
            \hfill St. Louis, MO\\
            \textit{\textbf{Software Engineering Intern}}
            \hfill May. 2019 --- Aug. 2019
            \begin{itemize}
                  \item[\textbullet] Created full-stack updates for internal tool used 700,000 times a day using JavaScript and Java
                  \item[\textbullet] Performed inquiries and patches for long-standing bugs and stability issues affecting thousands of staff members
            \end{itemize}

      \item[] \textbf{Missouri S\&T --- ACM}
            \hfill Rolla, MO\\
            \textit{\textbf{ACM Web Chair}}
            \hfill Jan. 2020 --- Present
            \begin{itemize}
                  \item[\textbullet] Managed 14 engineers in building websites and tools for our ACM branch resulting in better
                        recruitment, advertising, and analytics.
                  \item[\textbullet] Built full-stack features for ACM's services in TypeScript, React.js, and Koa.js
            \end{itemize}
\end{itemize}

\vspace*{-11px}
\subsection*{Notable Projects:}
\vspace*{-4px}
\textit{All projects listed below (and many more) on my GitHub}
\begin{itemize}

      \item[] \textbf{ShamHacks 2018 --- VeterIn:} (Received 2nd Place out of 50 teams)
            \hfill Feb. 2018\\
            \textit{Business focused network for Military Veterans to find jobs or employees}
            \begin{itemize}
                  \item[\textbullet] Wrote API for storing Veterans and Veteran-owned companies in Python
                  \item[\textbullet] Used Leaflet.js to map nearby Veteran businesses
            \end{itemize}

      \item[] \textbf{Personal Project --- Swoly:}
            \hfill Jan. 2018 - Dec. 2020\\
            \textit{Fitness app and terminal system to compute ideal workouts based on personal bests}
            \begin{itemize}
                  \item[\textbullet] Developed for iOS and Android in React Native
            \end{itemize}
\end{itemize}

\vspace*{-11px}
\subsection*{Technical Skills:}
\vspace*{-4px}
\textit{Listed in descending order of familiarity}
\vspace*{4px}

\begin{addmargin}[22pt]{0em}
      \begin{tabular*}{\textwidth - 22pt}{@{\extracolsep{\fill} } l l l l l l l l}
            \textbf{Languages:} & TypeScript & Python & C++ & Golang & Bash & R \\
            \textbf{Tools:} & Git & Unix & Unit Testing & Cloud Computing & \LaTeX & Vim
      \end{tabular*}
\end{addmargin}

\vspace*{-11px}
\subsection*{Honors and Activities:}

\begin{itemize}
      \item[] ACM Vice President Internal
            \hfill Apr. 2018 - Apr. 2019\\
            \textit{Managed 7 organizations in funding, time-lines, and planning for events hosting 120+ attendees}
      \item[] Megaminer AI
            \hfill Dec. 2017\\
            \textit{2nd place among 30+ other teams --- Programmed a game AI in Python}
      \item[] Local Hack Day
            \hfill Dec. 2017\\
            \textit{2nd place --- Developed a multi-threaded Golang chat server which also implemented multiplayer pong}
\end{itemize}

\end{document}
